Supplementary Material for Asymmetry paper

### 2020-03-13 Supplementary/Sup_mat.Rmd
updated sup mat

---
title: "Supplementary Material for Asymmetry paper"
author: "Warren James"
output: 
  bookdown::pdf_document2:
    fig_caption: false
---

---
title: "Supplementary Material For Asymmetry paper"
author: "Warren James"
date: "18/12/2019"
output: html_document
---

```{r setup, include=T, message=F, warning=F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
```

# Resampling
For experiments 1, 3, and 4 we made use of resampling existing data as we had run experiments in the past that were comparable. Experiment 2 was slightly different in that we did not have previous data to compare to, as such, we generated a series of distributions based on previous data and how reliably we could detect small differences. Resampling was carried out in order to establish if adding more pariticipants to our sample sizes would have lead to a reduction in uncertainty around our estimates.

@@

```{r make plots, include = T, echo = F}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())

@@

# Two Throws and Reward
As the hypothesis for both of these experiments was that out intervention would push participants towards being more optimal, we can use the same datasets to look at how uncertainty around the difference would change with varying sample sizes. For these experiments, comparison data was drawn from two unpublished studies; one in which the standard behaviour was observed, and one in which participants were closer to optimal in their performance.

@@

>>>>

---
title: "Supplementary Material for Asymmetry paper"
output: 
  bookdown::pdf_document2:
    fig_caption: false
---

---
title: "Supplementary Material For Asymmetry paper"
output: html_document
---

```{r setup, include=T, message=F, warning=F, echo= F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
```

# Resampling
For experiments 1, 3, and 4 we made use of resampling existing data as we had run experiments in the past that were comparable. Experiment 2 was slightly different in that we did not have previous data to compare to, as such, we generated a series of distributions based on previous data. Resampling was carried out in order to establish if adding more pariticipants to our sample sizes would have lead to a reduction in uncertainty around our estimates.

@@

```{r make plots, include = T, echo = F}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) +
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())

@@

## Two Throws and Reward
As the hypothesis for both of these experiments was that out intervention would push participants towards being more optimal, we can use the same datasets to look at how uncertainty around the difference would change with varying sample sizes. For these experiments, comparison data was drawn from two unpublished studies; one in which the standard behaviour was observed, and one in which participants were closer to optimal in their performance.

@@

```{r load in data and draw distributions, include = T, echo = F}
# so we're interested in the difference between the closest and furthest... 
# so we should just plot that? 
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")
plt_data <- df_all %>%
  filter(standard_lab %in% c("10%","90%")) %>%
  group_by(participant, condition, standard_lab) %>% 
  summarise(norm_pos = mean(norm_pos)) %>%
  ggplot(aes(standard_lab, norm_pos,
             colour = condition,
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  scale_y_continuous("Normalised Placement") +
  theme(axis.title.x = element_blank()) + 
  guides(colour = guide_legend(title = "Condition"),
         fill = guide_legend(title = "Condition"))

plt_data_diff <- plt_data[["data"]] %>%
  ungroup() %>% 
  spread(standard_lab, norm_pos) %>% 
  mutate(diff = `90%` - `10%`) %>% 
  ggplot(aes(condition, diff,
             colour = condition, 
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1))

# plot samples in terms of difference? 
plt_hdi <- df_sample %>% 
  filter(n_trials != 12) %>%
  mutate(diff = baseline - comparison) %>% 
  group_by(n_subs, dist_type) %>% 
  summarise(mu = mean(diff),
            upper = hdi(diff)[2],
            lower = hdi(diff)[1]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower, ymax = upper),
              alpha = .3) + 
  facet_wrap(~dist_type) + 
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Difference: Athletes - Avatar")

# show both 
gridExtra::grid.arrange(plt_data, plt_hdi, ncol = 1)
